Social Visual Analytics: DevOps for Data Scientists

### 2015-03-20 introduction.tex
fix bib things

Further afield, {\bf Electronic Lab Notebooks} are applications for organizing
and sharing data from scientific lab experiments\cite{Rubacha:ELN:2011}.
In a sense, we hope to adapt and extend this concept to the work of
visual analytics teams.

>>>>

Further afield, {\bf Electronic Lab Notebooks} are applications for organizing
and sharing data from scientific lab experiments\cite{Rubacha:2011:ELN}.
In a sense, we hope to adapt and extend this concept to the work of
visual analytics teams.
